Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Reformatted hard wrap for text

In the present research, we investigate the relationship between linguistic cohesion and social cohesion in times of social conflict and unrest. We tackle a question related to the one posed by Zeitzoff (2017): how does social media reflect on-the-ground realities during times of social conflict [@Zeitzoff_2017]? We examine patterns of linguistic cohesion on Twitter during the Arab Spring uprising in Syria between March and June 2012. We contextualize the linguistic cohesion with social mobilization and response to the relative intensity of the conflict. Cohesion is a multi-layered concept referring to the connectedness of words, thoughts, speakers, and actions. Cohesion reflects the continuity of language and expression, and it shows the connectivity of participants in a social movement. To address the relationship between language and discourse and social movements, we adopt an interdisciplinary approach that incorporates linguistics, psychology, and political science using non-linear dynamical systems methodology to model the relationship between language and action. We find that in the early months of 2012, conflict-related events were more strongly associated with linguistic cohesion than were more neutral or peaceful events.

@@

#### Metrics
Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
respective window. For these analyses, we decided to focus on recurrence rate 
and determinism.

@@

For social cohesion and count of positive events, we saw a downward trend in 
RR as the window advances throughout the sample. Interestingly, we see
largely above-chance RR until the 50th window, with some exceptions during
window periods 20-30. DET was at or above chance for the 7th--17th, 32nd-34th, 
and 60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

>>>>

In the present research, we investigate the relationship between linguistic
cohesion and social cohesion in times of social conflict and unrest. We tackle a
question related to the one posed by Zeitzoff (2017): how does social media
reflect on-the-ground realities during times of social conflict
[@Zeitzoff_2017]? We examine patterns of linguistic cohesion on Twitter during
the Arab Spring uprising in Syria between March and June 2012. We contextualize
the linguistic cohesion with social mobilization and response to the relative
intensity of the conflict. Cohesion is a multi-layered concept referring to the
connectedness of words, thoughts, speakers, and actions. Cohesion reflects the
continuity of language and expression, and it shows the connectivity of
participants in a social movement. To address the relationship between language
and discourse and social movements, we adopt an interdisciplinary approach that
incorporates linguistics, psychology, and political science using nonlinear
dynamical systems methodology to model the relationship between language and
action. We find that in the early months of 2012, conflict-related events were
more strongly associated with linguistic cohesion than were more neutral or
peaceful events.

@@

#### Metrics
For WCRQA analyses, we decided to focus on RR and DET.

@@

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 50th window, with some exceptions during window
periods 20-30. DET was at or above chance for the 7th--17th, 32nd--34th, and
60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
